%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Team Lead}
    {Lowe's Companies, Inc.}
    {Charlotte, NC (Remote)}
    {Mar. 2021 - Present}
    {
        \begin{cvitems}
            \item {Formed and trained a team of developers to work with a modern Java tech stack, utilizing current coding \\conventions such as Java streams and popular libraries including Lombok, Jackson, MapStruct, Project \\Reactor, and Micronaut.}
            \item {Lead said team through day-to-day operations, administrating stand-up, refining and assigning stories, \\performing code reviews, and holding high-level design discussions with developers and product  owners.}
            \item {Onboarded new employees to codebase and framework, organizing and participating in KT sessions to \\ensure smooth transition to the team.}
            %\item {Analyzed and solved high priority service issues in a multinational production environment.}
        \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Software Engineer}
    {Lowe's Companies, Inc.}
    {Charlotte, NC (Remote)}
    {Apr. 2020 - Mar. 2021}
    {
        \begin{cvitems}
            \item {Built from the ground up a new RESTful microservice API utilizing the Micronaut framework to handle retail \\sales company-wide.}
            \item {Analyzed and solved high priority service issues in a multinational production environment.}
            \item {Refactored codebase to streamline logic, increase readability, and enhance system performance.}
            \item {Wrote unit, functional, and end-to-end tests to validate application behavior.}
        \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Nuclear Application Analyst}
    {Duke Energy}
    {Charlotte, NC}
    {Aug. 2019 - Apr. 2020}
    {
        \begin{cvitems}
            \item {Worked with a small, AGILE team to deliver a new product designed to increase efficiency within nuclear \\operations.}
            \item {Interacted with a team of developers and users to rethink design concepts and enhance the user experience.}
            \item {Developed back-end services in Java, SQL, and NextAxiom to integrate with pre-existing systems.}
        \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {System Administrator and Software Engineer}
    {Bio-Moliere}
    {Clemson, SC}
    {Jan. 2018 - Jun. 2018}
    {
      \begin{cvitems}
        \item {Migrated a graduate school project from the Palemetto 2 compute cluster to AWS, utilizing Docker containers.}
        \item {Implemented an EC2 API and webpage for accessing the project.}
        \item {Developed a scalable, portable system for launching instances of the software within AWS Batch.}
        \item {Utilized S3 for archiving primary files, as well as EFS to enable heavily parallelized access of core data files.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
